Analysis-ready VCF at Biobank scale using Zarr

### 2025-03-05 paper.tex
Add AoU dataset details

% Your manuscript lacks a 'Data availability' section and we require it; could
% you please create one and list all the datasets you have used in your case
% studies along with direct URLs (better: DOIs, if available) to these datasets
% (not the associated manuscript, but directly the dataset's main page, for user
% accessibility purposes).
The datasets used for the case studies in this article are described/available at:
Genomics England aggV2: \url{https://re-docs.genomicsengland.co.uk/aggv2/};
Future Health Data Release 9: 
\url{https://ourfuturehealth.gitbook.io/our-future-health/data/data-releases/2024-data-releases/release-9};
All of Us: \url{https://www.researchallofus.org/data-tools/data-snapshots/};
Norway Spruce: data release pending;
SARS-CoV-2 Viridian: \url{https://doi.org/10.6084/m9.figshare.28360031.v2}.

>>>>

% Your manuscript lacks a 'Data availability' section and we require it; could
% you please create one and list all the datasets you have used in your case
% studies along with direct URLs (better: DOIs, if available) to these datasets
% (not the associated manuscript, but directly the dataset's main page, for user
% accessibility purposes).
The datasets used for the case studies in this article are described/available at:
Genomics England aggV2: \url{https://re-docs.genomicsengland.co.uk/aggv2/};
Future Health Data Release 9: 
\url{https://ourfuturehealth.gitbook.io/our-future-health/data/data-releases/2024-data-releases/release-9};
All of Us CDRv7:
\url{gs://fc-aou-datasets-controlled/v7/wgs/short\_read/snpindel/acaf\_threshold_v7.1/vcf/},
described at 
\url{https://support.researchallofus.org/hc/en-us/articles/4616869437204-Controlled-CDR-Directory-Archived-C2022Q4R13-CDRv7};
Norway Spruce: data release pending;
SARS-CoV-2 Viridian: \url{https://doi.org/10.6084/m9.figshare.28360031.v2}.
